A function--sheaf dictionary for algebraic tori over local fields

### 2013-10-10 shanghai.tex

  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
  First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
  Let $k'/k$ be any degree-$n$ extension and let $\Nm : k'\to k$ be the norm map. 
  By \cite{laumon:87a}*{1.1.3.3}, 
  \[
  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm;
  \]
  on the other hand, 
  \[
  \trFrob{\qcs{L}} \circ \Nm = \trFrob{(G_{k'}\hookrightarrow G)^*\qcs{L}},
  \]
   by Proposition~\ref{prop:basechange}.
  Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
  This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
  Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
  it follows that $L_G$ is an equivalence.
\end{proof}

>>>>

  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
  First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
  Let $k'/k$ be any degree-$n$ extension; 
  let $\Nm : G(k')\to G(k)$ be the norm map 
  and let $b : G_{k'} \to G$ be the base change map.
  By \cite{laumon:87a}*{1.1.3.3}, 
  $\trFrob{b^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm$;
  on the other hand, $\trFrob{\qcs{L}} \circ \Nm = \trFrob{b^*\qcs{L}}$,
   by Proposition~\ref{prop:basechange}.
  Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
  This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
  Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
  it follows that $L_G$ is an equivalence.
\end{proof}
